% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
\usepackage{amsmath}
\usepackage{hyperref}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Distributed Teams Are Founded on Explicit
Communication Channels}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Het Jatin Dalal}
%

%
\institute{Computer Science and Software Engineering , Concordia University \\ 
\vspace{10pt}  VCS: Github: \href{https://github.com/Het95/40200513-SOEN6481-TAS}{https://github.com/Het95/40200513-SOEN6481-TAS}}

%
%
\maketitle              % typeset the header of the contribution
%

\begin{abstract}
    The abstract should briefly summarize the contents of the paper in
    15--250 words.
    
    \keywords{First keyword  \and Second keyword \and Another keyword.}
    \end{abstract}
    %
    %
    %
    \section{Introduction}
    \subsection{Motivation}
    The motivation for researching "Distributed Teams Established on Explicit Defined Communication Channels" stems from a number of key considerations and the difficulties of modern work contexts.
    
    \begin{enumerate}
        \item \textbf{Surge in popularity of Distributed Team}: The majority of businesses with growing workforces are shifting to distributed team structure, particularly in light of recent pandemics like COVID-19. This makes it much more important in such an environment to collaborate and communicate effectively.. 
        \item \textbf{Accountability}: Having clear channels of communication within the team facilitates awareness of individual roles and responsibilities.
        \item \textbf{Collaboration}: Distributed teams can share project-related materials and do various other project management tasks with each other when they have clear communication channels. 
        \item \textbf{Embrace, Evolve, Adjust}: One must adjust to the changing environment due to changes in new technology, team and company sizes, and the organization can concentrate more on this by employing clear communication channels.
    \end{enumerate}
    
    \subsection{Problem Statement} Due to the larger team size, the distributed team finds it difficult to communicate in person.Also, there are other problems like interrupting coworkers to find resources can waste time, especially when someone is intensely focused and productive. This makes it necessary to create channels for communication, but there was discussion about whether to use synchronous or asynchronous channels—each having advantages and being able to be selected based on necessity. Therefore, the key to achieving quick growth and productivity in a dispersed team setting is to establish a written communication culture and select clear communication channels.
    
    \subsection{Objectives}
    
\end{document}
